
## Problem 1

**1. Clear Lake has surface area of 708,000 m2 (70.8 ha).  For a given month, the lake has an inflow of 1.5 m3/s and an outflow of 1.25 m3/s.  A +1.0-m storage change, or increase in lake level was recorded.  If a precipitation gage recorded a total of 24 cm for this month, determine the evaporation loss (in cm) for the lake.  Assume that seepage (deep drainage) loss is negligible.  (10 pts)**

```{r cars}
Area_m2 <- 708000 #m2
Area_ha <- 70.8 #ha
inflow <- 1.5 #m3/s
outlow <- 1.25 #m3/s
Storage_change <- 1 #m
Storage_change_cm <- Storage_change*100 #m
Precip <- 24 #cm

#determine evaporation loss (in cm) for the lake
#Assume that deep drainage loss is negligible 

#Area to cm2
Area_cm2 <- Area_m2 * 10000

#Volume of precipitation
P_volume_cm3months <- Area_m2 * 1000 * Precip

#Runoff
RO_m_s<- (inflow - outlow)/Area_m2 #m/second
RO_m_s #runoff m/s

#Turn to month
RO_cm_month <- RO_m_s * 2.628e+8 #conversion from m/sec to cm/month
RO_cm_month #runoff cm/month

#Meters to cm

```

Solving for et we will have

$$ et(t) = p(t) + R0 - S$$
Solving 
```{r}

et <- Precip + RO_cm_month - Storage_change_cm

et 

#Et is 16.7 cm/month
```


## Problem 2
