---
title: "Problem Set 2 - Watershed Hidorlogy"
author: "Emilio Aguilar"
date: '2022-09-18'
output: pdf_document
---

```{r setup, include=FALSE}
#Libraries
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

**1. Clear Lake has surface area of 708,000 m2 (70.8 ha).  For a given month, the lake has an inflow of 1.5 m3/s and an outflow of 1.25 m3/s.  A +1.0-m storage change, or increase in lake level was recorded.  If a precipitation gage recorded a total of 24 cm for this month, determine the evaporation loss (in cm) for the lake.  Assume that seepage (deep drainage) loss is negligible.  (10 pts)**

```{r cars}
Area_m2 <- 708000 #m2
Area_ha <- 70.8 #ha
inflow <- 1.5 #m3/s
outlow <- 1.25 #m3/s
Storage_change <- 1 #m
Precip <- 24 #cm

#determine evaporation loss (in cm) for the lake
#Assume that deep drainage loss is negligible 

#Area to cm2
Area_cm2 <- Area_m2 * 10000

#Volume of precipitation
P_volume_cm3months <- Area_m2 * 1000 * Precip

#Cubic pero second to cubic per month
#Multiply the value of volum/time by 2.628e+12
inflow_cm3month <- inflow * 2.628e+12
outlow_cm3month <- outlow * 2.628e+12


#Runoff
RO_cm3month <- inflow_cm3month - outlow_cm3month

```

Evapotraspiration may be estimated with a water balance approach. if the change in storage and all the inputs and outputs are known 

$$ dV/dt = p(t) + rsi(t) + rgi(t) - rso(t) - rgo(t) - et(t)$$
Where, V is the average volume of water stored, p is precipitation rate, rsi is average surface water inflow rate, rgi average ground inflow rate rso average surface water outflow rate, rgo average groundwater outflow rate and et average transportation. If groundwater flow is negligible we will have:

$$ dV/dt = p(t) + ΔRO- et(t) $$
Solving for et we will have

$$ et(t) = p(t) + R0 $$
Solving 
```{r}

#Volume of flow (discharge) 
dis_cmmonth <- RO_cm3month/Area_cm2

et <- Precip - dis_cmmonth 
et 
#Et is 68.7 cm/month
```
