---
title: "Problem 3 Watershed Hidrology"
author: "Emilio Aguilar"
date: '2022-09-27'
output: pdf_document
---
```{r setup, include=FALSE}
#Libraries
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
```

# 1 - Penman Potential Evapotranspiration

## 1.1 Data
```{r}
Tavg_Aug2 <- 18.6 #Celsius 
Tma_Aug2  <- 24.4 #Celsius
Tmin_Aug2 <- 12.8 #Celsius
Tavg_Aug1 <- 15.0 #Celsius
Tavg_Aug3 <- 20.6 #Celsius
VPD = 1.0927 #kPa
U2 = 1.83 #ms1
Rn = 10.63 #MJ m-2 day-1
H = 213.4 #m
lat = 41 #N

```


## 1.2 What is your calculated G? 
G is the ground heat flux messured in MJ m^-1^ day^-1^

$$ G = 4.2 * (T~{i+1} - T ~{i-1} )/Deltat $$

```{r}
#Select Variables
Tbefore <- Tavg_Aug1
Tafter <- Tavg_Aug3 
time <- 3 - 1 

#Solution
G <- 4.2 * ((Tbefore - Tafter)/time)

print(paste("The ground heat flux is",G,"MJ m-1 day-1"), quote = FALSE)
```


## 1.3 What is your calculated Lambda?    
Lambda is the latent heat of vaporization in MJ kg^-1^, where T is average temperature (I assumed of the 3 days)

$$ Lambda = 2.501 - 2361* 10^{-3} * T $$

```{r}
#Data
AvgT <- mean(c(Tavg_Aug1,Tavg_Aug2,Tavg_Aug3))

#Solution
Lambda <- round(2.501 - 2361* 10^{-3} * AvgT,2)

print(paste("The latent heat of vaporization is",Lambda,"MJ kg-1"), quote = FALSE)
```

## 1.3 What is your calculated P? 
P is atmospheric pressure measure in kPA, H is the elevation above sea level in meters.

$$P = 101.3 - 0.01055H$$

```{r}
#Data
H <- H #elevation above sea level

#Solution
P <- round(101.3 - 0.01055 * H,2)

print(paste("The atmospheric pressure is",P,"Kpa"), quote=FALSE)
```

## 1.4 What is your calculated Gamma?
Gamma is the pyschrometric constant measured in kPa C^-1^, cp is the specific heat of water at constant pressure (0.001013 kJ kg-1 oC-1) and P is atmospheric pressure

$$Gamma = C~{p} *P/0.622*Lambda $$

```{r}
#Data
CP <- 0.001013 #kg-1 oC-1

#Solution
Gamma <- round(CP * P / 0.622 * Lambda,2)

print(paste("The pyschrometric constant is",Gamma,"kPa C-1"), quote = FALSE)
```

## 1.5 What is your calculated Delta?
Delta is the slope of the saturation vapor pressure - temperature curve, mesured in kPa C^-1^


$$ Delta = 0.200(0.00738T + 0.8072)^7 - 0.00116 $$

```{r}
#Data
#AvgT

#Solution
Delta= round(0.200 * (0.00738*AvgT + 0.8072)^7 - 0.00116,2)

print(paste("The slope of curve is",Delta,"kPa C-1"), quote=FALSE)
```


## 1.6 What is your calculated PET?
PET is potential evapotranspiration in mm day^-1

```{r}
#Solution 
#First Part of the equation

PET_1 <- Delta / (Delta + Gamma) * (Rn - G)
PET_2 <- Gamma/ (Delta + Gamma) * 6.43 * (1 + 0.53 * U2) * VPD

PET <- round((PET_1 + PET_2) / Lambda,2)

print(paste("The potential evapotranspiration is",PET,"mm per day"), quote=FALSE)
```


# 2 - The Evaporation Pan

## 2.1 Data

## 2.2 Solution
Evaporation is computed as the difference between observed levels, adjusted for any measured precipitation (or other added water).  

If the level on day 1 was measured at 7.8 in and the level on day two was measured at 7.6 in, and precipitation on day 2 was 0.1 in, what was the evaporation from the pan?

```{r}

day1 <- 7.8 #inches
day2 <- 7.6 #inches
Preciptiation <- 0.1 #inches

EV <- day1 - day2 + Preciptiation

```

```{r, echo=FALSE}
print(paste("The evaporation from the pan was",EV,"inches"), quote = FALSE)
```


